MultiDataImportPico

### 2023-12-06 Code/MultiDataImportPico.Rmd
Fixed import to read unzipped file.

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCulti")
DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")

@@

MultiFiles <- list.files(path = DataIn, pattern = Project, full.names = TRUE)

#check file names
MultiFiles

@@

```{r set TargetFile}
TargetFile <- "../MultiCultiData/20230413_PICO_MCMIX004_RUN113.csv"

TargetFileName <- str_split(string = TargetFile, "/")[[1]][3] %>%
  str_remove(pattern = ".csv")

TargetFileName
```

@@

```{r metadata merge}
#This generates 'NA' values for ~1,000,000 rows of 'O2'; possibly the temperature rows?
TargetDataMeta <- left_join(x = TargetDataWide, y= Catalog, by = c("ExpDate", "MC", "Tube"), suffix  = c("_multi", "_cat"))

@@

TargetDataMetaFilter <- TargetDataMeta %>%
  filter(OD680 > 0) %>% # consider this rule for OD720 as well
  group_by(ID) %>%
  arrange(Filename, MC, Tube, time) %>%
  mutate(ExpEndHour = (difftime(ExpEndDate, StartDate, units = "hours"))) %>%
   mutate(TimeFlag = case_when(time >= ExpEndHour  ~ 1, 
                              time < ExpEndHour ~ 0)) %>%
  mutate(MovMedian680 = rollapply(OD680, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMedian720 = rollapply(OD720, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMAD680 = rollapply(OD680, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         MovMAD720 = rollapply(OD720, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         IsMovMAD680Outlier = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), 1,0),
         IsMovMAD720Outlier = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), 1,0))

@@

```{r filterdataplotexpand}
#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 1
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) 
Light_x = max(TargetDataMetaFilter$time) + 100

@@

TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  # coord_cartesian(xlim = c(0, 800)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")

>>>>

```{r set project variables}
#"..", takes up a level in the directory path
Project <- "PICO"
DataIn <- file.path("..", "Data", "RawData", "MultiCultiData.zip")
DataOut <- file.path("..","Data", "ImportedData", "MultiCultiData")

@@

unzip(DataIn, list = TRUE)

#check file names

@@

```{r set TargetFile}

TargetFile <- unzip(DataIn, "20211223_PICO_MCMIX006_RUN42.csv")

TargetFileName <- str_remove(string = TargetFile, pattern = ".csv")

TargetFileName

@@

```{r metadata merge}
#This generates 'NA' values for ~1,000,000 rows of 'O2'; possibly the temperature rows?
TargetDataMeta <- left_join(x = TargetDataWide, y= CultureCatalog, by = c("ExpDate", "MC", "Tube"))

@@

TargetDataMetaFilter <- TargetDataMeta %>%
  # filter(OD680 > 0) %>% # consider this rule for OD720 as well
  group_by(ID) %>%
  arrange(Filename, MC, Tube, time) %>%
  mutate(ExpEndHour = (difftime(ExpEndDate, StartDate, units = "hours"))) %>%
   mutate(TimeFlag = case_when(time >= ExpEndHour  ~ 1, 
                              time < ExpEndHour ~ 0)) %>%
  mutate(MovMedian680 = rollapply(OD680, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMedian720 = rollapply(OD720, MovAvgWindow, median, fill = "extend",  align = "left"),
         MovMAD680 = rollapply(OD680, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         MovMAD720 = rollapply(OD720, MovAvgWindow, mad, fill = "extend",  align = "left"), 
         IsMovMAD680Outlier = if_else(OD680 > MovMedian680 + (MovMAD680 * MovAvgScreen) | OD680 < MovMedian680 - (MovMAD680 * MovAvgScreen), 1,0),
         IsMovMAD720Outlier = if_else(OD720 > MovMedian720 + (MovMAD720 * MovAvgScreen) | OD720 < MovMedian720 - (MovMAD720 * MovAvgScreen), 1,0))

@@

```{r filterdataplotexpand}

#labelling dynamically offset from data traces.
#use 'median' for 'x' and OD680 + offset for 'y'
ExpandTube = 1
OD680_x = median(TargetDataMetaFilter$time)
OD720_x = median(TargetDataMetaFilter$time) 
Light_x = max(TargetDataMetaFilter$time) + 100

@@

TargetDataMetaFilter %>% 
  filter(Tube == ExpandTube) %>%
  ggplot() +
  geom_point(aes(x = time, y = OD680, colour = as.factor(WL)), size = 0.1) +
  geom_point(aes(x = time, y = OD720), size = 0.1, alpha = 0.1, colour = "blue") +
  scale_colour_manual(values = MCMIXColours) +
  geom_point(aes(x = time, y = Actinic_par/1000), colour = "orange",  size = 0.0001) +
   geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
  geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  # scale_x_continuous(breaks=seq(0, 800, by = 125)) +
  # coord_cartesian(xlim = c(0, 800)) +
  labs(y = "Optical Density (OD)", x = "Elapsed Time (h)",subtitle = "Growth Light (µE); Strain; ID; Tube") +
  # facet_grid(rows = vars(O2), cols = vars(Tube, Par_ue, Strain, ID)) +
  annotate(geom = "text", x = OD680_x, y = OD680_y, label = "OD680", size = 5, colour = "darkblue") +
  annotate(geom = "text", x = OD720_x, y = OD720_y, label = "OD720", size = 5, colour = "black") +
  annotate(geom = "text", x = Light_x, y = Light_y, label = "Light level", size = 5, colour = "orange") +
  theme_bw() +
  labs(colour = "Actinic PAR (nm)")
